Who Cares About Crackdowns? Exploring the Role of Trust in Individual Philanthropy

### 2020-10-01 manuscript/manuscript.Rmd
Move lonely footnote with the others

In our experiment, we presented respondents with four randomly selected international nonprofit organizations with four randomly assigned features.^[See the appendix for a copy of the survey.] We included organizations that are associated with a range of contentious and noncontentious issues: Amnesty International, Greenpeace, Oxfam, and the International Committee of the Red Cross. Because of their strong name recognition, these organizations (and others like World Vision, the World Wildlife Fund, and Médecins Sans Frontières) are commonly used in experimental surveys on philanthropy [@FaulknerTruongRomaniuk:2015].

@@

An organization's relationship with its host government does influence market shares across levels of income, but the size of this difference depends on the magnitude of income. When splitting income based on the US median income (\$61,372), there is no difference between income levels. In general, personas prefer to donate to organizations with friendly relationships with their host governments and avoid those that are criticized or under crackdown. However, instead of looking at personas with below- and above-median incomes, we can simulate a subset of wealthier donors that earn at least \$100,000 annually. These personas are more likely to prefer donating to organizations that are criticized by their host governments. This falls in line with their preference for human rights organizations, which have more contentious missions and are more likely to receive government criticism. This support, however, appears to evaporate as civil society crackdown intensifies. High income personas are the least likely demographic to prefer donating to NGOs under crackdown. Their lower income counterparts, on the other hand, are generally unfazed by NGOs' relationships with government, maintaining the same average market share across all three types of host country relationships. Patterns in preferences for issue area and funding sources remain constant across both methods of categorizing income—crackdown only has an effect on very high income personas. Income thus appears to influence preferences particularly for NGOs facing criticism and crackdown abroad—wealthy donors are perhaps fair-weather friends that are more likely to pull their support when an organization's work becomes more difficult.

@@

>>>>

In our experiment, we presented respondents with four randomly selected international nonprofit organizations with four randomly assigned features.[^appendix-survey] We included organizations that are associated with a range of contentious and noncontentious issues: Amnesty International, Greenpeace, Oxfam, and the International Committee of the Red Cross. Because of their strong name recognition, these organizations (and others like World Vision, the World Wildlife Fund, and Médecins Sans Frontières) are commonly used in experimental surveys on philanthropy [@FaulknerTruongRomaniuk:2015].

@@

An organization's relationship with its host government does influence market shares across levels of income, but the size of this difference depends on the magnitude of income. When splitting income based on the 2017 US median income (\$61,372), there is no difference between income levels. In general, personas prefer to donate to organizations with friendly relationships with their host governments and avoid those that are criticized or under crackdown. However, instead of looking at personas with below- and above-median incomes, we can simulate a subset of wealthier donors that earn at least \$100,000 annually. These personas are more likely to prefer donating to organizations that are criticized by their host governments. This falls in line with their preference for human rights organizations, which have more contentious missions and are more likely to receive government criticism. This support, however, appears to evaporate as civil society crackdown intensifies. High income personas are the least likely demographic to prefer donating to NGOs under crackdown. Their lower income counterparts, on the other hand, are generally unfazed by NGOs' relationships with government, maintaining the same average market share across all three types of host country relationships. Patterns in preferences for issue area and funding sources remain constant across both methods of categorizing income—crackdown only has an effect on very high income personas. Income thus appears to influence preferences particularly for NGOs facing criticism and crackdown abroad—wealthy donors are perhaps fair-weather friends that are more likely to pull their support when an organization's work becomes more difficult.

@@

[^appendix-survey]: See the appendix for the full text of the survey.
